{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-01 thesis/landslide.tex
TRUSTED_THR_JOIN

@@

\subsubsection{Happens-before}

>>>>

	\item {\tt TRUSTED\_THR\_JOIN=0} - if set to 1, forces Landslide to add a happens-before edge (\sect{\ref{sec:landslide-dpor-hb}}) between the exiting of some thread $N$ and the end of any subsequent {\tt thr\_join}$(N)$ call,
		even if that {\tt join} would not ordinarily block.
		This is useful for state space reduction when testing threaded client code;
		for example,
		in the interleaving
		TID1: {\tt x++; thr\_exit();},
		TID2: {\tt thr\_join(1); print(x);},
		%this {\tt join} will wait on no condition variables, just take a few uncontended mutexes, reap the thread,
		%and go along on its way, so
		DPOR, not automatically trusting {\tt join}'s behaviour,
		will attempt to test the TID2, TID1 interleaving to reorder the accesses on {\tt x},
		whereupon {\tt join} will block, forcing these interleavings to be equivalent.
		% if you had tested them in the other order to begin with, dpor would detect this dependency,
		% and would skip the other equivalent interleaving
		This option allows DPOR to skip checking that {\tt join} behaves properly
		and prune the second interleaving
		by teaching it the expected blocking semantics. %to begin with.
		Obviously, not for use when actually testing {\tt thr\_join} itself!

@@

\subsubsection{Happens-before}
\label{sec:landslide-dpor-hb}
